Memory-aware Adaptive Scheduling of Scientific Workflows on Heterogeneous Architectures\\

### 2025-03-11 main.tex
temp

\noindent{\bf HEFT-based algorithms. }
%\subsection{Static list schedulers, especially HEFT-based algorithms}
%\label{sub:static-list-schedulers}
%
Introduced in 2002, HEFT~\cite{topcuoglu2002performance} is a list-based heuristic, consisting 
%HEFT and its successors consist 
of two phases: task prio\-ri\-tization/ordering and task assignment.
In the first phase, the algorithms compute bottom levels of the tasks based on some priorities (create the list),
and then schedule tasks in the order of these priorities.
The modifications of HEFT revolve around the way the priorities of the tasks are computed and the logic of the processor assignment.
All such algorithms assume a heterogeneous execution environment.

@@

\medskip
%\subsection
\noindent{\bf Memory-aware scheduling algorithms. }
%\label{sub:mem-aware-algs}
%
%Only memory-aware scheduling algorithms are designed to respect memory constraints.
%%Respecting processor memories adds a constraint to a scheduling problem.
%%Therefore, only specifically memory-targeted algorithms address this issue.
%Moreover, 
The way processor memories are represented in the model has a decisive impact on the way the constraint
is formulated and addressed in the algorithm.
%
Different models of memory available on processors and memory requirements of tasks have been presented.

@@

%    \subsection
\smallskip
\noindent{\bf Dynamic/adaptive algorithms. }
We finally review related work in a dynamic setting. With no variation in task parameters, 
    DVR HEFT~\cite{SANDOKJI2019482} rather considers that new tasks arrive in the system. 
    They use an almost unchanged HEFT algorithm in the static step, executing three slightly
    varying variants of task weighting and choosing the variant that gives the best overall makespan.
%    In the dynamic phase, they receive new tasks and schedule them on either idle processors or 
%    those processors that give them
%    the earliest finish time.
%    %Task failures are not covered.
%
%    Rahman~\etal 
    The dynamic critical path (DCP) algorithm for grids maps tasks to machines
    by calculating the critical path in the graph dynamically at every step~\cite{rahman2013}.
    %For all tasks they compute the earliest start time and absolute latest start time that are upper and lower bounds
    %on the start time of a task (differing by the slack this task has).
    %All tasks on this critical path have the same earliest and latest start times, because they cannot be delayed.
    The authors schedule the first task on the critical path to the best suitable processor and recompute the critical path.
    %The algorithm takes the first unscheduled task on the critical path each time and maps it on a processor identified for it.
    %If processors are heterogeneous, then the start times are computed with respect for the processor, and the minimum
    %execution time for the task is chosen.
    The heuristic also uses the same processor to schedule parent and children tasks, as to avoid data transfer between processors.
%    The approach is evaluated on random workflows of the size up to 300 tasks.

@@

\subsection{Dynamic experiments on the memory-constrained cluster}
\label{sec.expe.dyn}
\new{In this section, we try to assess the advantage of the dynamic approach.
To this end, we compare the makespans of executions with and without recomputation.}
The makespan in case of no recomputation becomes invalid as soon as at least one task finds itself in an invalid memory size
situation -- that is, if the scheduler assumed the task's memory to be smaller than actually needed and
assigned the task to a processor with not enough memory capacity.
Due to an extremely constrained memory in this cluster, only 134 experiments out of 1160
(290 experiments for each of the 3 heuristics and the baseline \heft)
 \new{obtain a valid makespan when no recomputation is done}.

In the case of \heft, $14$ valid initial makespans were computed.
Out of them, $13$ remain valid \new{until the end of an execution with recomputation},
\new{i.e., the schedule is still valid when accounting for the final execution time of each task and their memory requirement.}
The same $13$ experiments end \new{valid in case of no recomputation, i.e. when following the initial schedule without ever recomputing it}.
Hence, these workflows require so few resources that
\new{the devations do not invalidate their schedules. However, there is also nothing to be gained by rescheduling them.}
%$13$ experiments ended with a valid makespan after recomputation in case of \heft, which corresponds to $4.4\%$ success
%rate. However, there were only $14$ successful \heft experiments overall in this setup, so for the successful experiments
%only, the success rate of not recomputing is $92\%$.

In case of \heftmm, all $290$ workflows can be scheduled initially \new{(static case)} and all these schedules remain valid until the end,
\new{when new schedules are computed in a dynamic way. However, only}
$16$ experiments end with a successful schedule without recomputation, a rate of~$5.5\%$.

@@

\new{
These results indicate that a meaningful comparison proves difficult due to
many invalid schedules. However, they still show that doing recomputation 
is beneficial for both makespan and the number of valid solutions.
}

>>>>

%\noindent{\bf 
\subsection{HEFT-based algorithms}
%\subsection{Static list schedulers, especially HEFT-based algorithms}
%\label{sub:static-list-schedulers}
%
Introduced in 2002, HEFT~\cite{topcuoglu2002performance} is a list-based heuristic, consisting 
%HEFT and its successors consist 
of two phases: task prio\-ri\-tization/ordering and task assignment.
In the first phase, the algorithms compute bottom levels of the tasks based on some priorities (create the list),
and then schedule tasks in the order of these priorities.
The modifications of HEFT revolve around the way the priorities of the tasks are computed and the logic of the processor assignment.
All such algorithms assume a heterogeneous execution environment.

@@

%\medskip
\subsection{
%\noindent{\bf 
Memory-aware scheduling algorithms}
%\label{sub:mem-aware-algs}
%
%Only memory-aware scheduling algorithms are designed to respect memory constraints.
%%Respecting processor memories adds a constraint to a scheduling problem.
%%Therefore, only specifically memory-targeted algorithms address this issue.
%Moreover, 
The way processor memories are represented in the model has a decisive impact on the way the constraint
is formulated and addressed in the algorithm.
%
Different models of memory available on processors and memory requirements of tasks have been presented.

@@

 \subsection{%
%\bigskip
%\noindent{\bf 
Dynamic/adaptive algorithms}
We finally review related work in a dynamic setting. With no variation in task parameters, 
    DVR HEFT~\cite{SANDOKJI2019482} rather considers that new tasks arrive in the system. 
    They use an almost unchanged HEFT algorithm in the static step, executing three slightly
    varying variants of task weighting and choosing the variant that gives the best overall makespan.
%    In the dynamic phase, they receive new tasks and schedule them on either idle processors or 
%    those processors that give them
%    the earliest finish time.
%    %Task failures are not covered.
%
%    Rahman~\etal 
    The dynamic critical path (DCP) algorithm for grids maps tasks to machines
    by calculating the critical path in the graph dynamically at every step~\cite{rahman2013}.
    %For all tasks they compute the earliest start time and absolute latest start time that are upper and lower bounds
    %on the start time of a task (differing by the slack this task has).
    %All tasks on this critical path have the same earliest and latest start times, because they cannot be delayed.
    The authors schedule the first task on the critical path to the best suitable processor and recompute the critical path.
    %The algorithm takes the first unscheduled task on the critical path each time and maps it on a processor identified for it.
    %If processors are heterogeneous, then the start times are computed with respect for the processor, and the minimum
    %execution time for the task is chosen.
    The heuristic also uses the same processor to schedule parent and children tasks, as to avoid data transfer between processors.
%    The approach is evaluated on random workflows of the size up to 300 tasks.

@@

\subsection{Dynamic experiments on the memory-constrained cluster}
\label{sec.expe.dyn}
\new{In this section, we try to assess the advantage of the dynamic approach.
To this end, we compare the makespans of executions with and without recomputation.}
The makespan in case of no recomputation becomes invalid as soon as at least one task finds itself in an invalid memory size
situation -- that is, if the scheduler assumed the task's memory to be smaller than actually needed and
assigned the task to a processor with not enough memory capacity.
Due to an extremely constrained memory in this cluster, only 134 experiments out of 1160
(290 experiments for each of the three heuristics and the baseline \heft)
 \new{lead to a valid makespan when no recomputation is done}.

In the case of \heft, $14$ valid initial schedules were computed.
Out of them, $13$ remained valid \new{until the end of an execution with recomputation},
\new{i.e., the schedule is still valid when accounting for the final execution time of each task and their memory requirement.}
The same $13$ experiments also led to \new{valid schedules in case of no recomputation, i.e., when following the initial schedule without ever recomputing it}. 
Indeed, these workflows required so few resources that
\new{the deviations did not invalidate their schedules. Also, there is also nothing to be gained by rescheduling them.}
%$13$ experiments ended with a valid makespan after recomputation in case of \heft, which corresponds to $4.4\%$ success
%rate. However, there were only $14$ successful \heft experiments overall in this setup, so for the successful experiments
%only, the success rate of not recomputing is $92\%$.

In case of \heftmm, all $290$ workflows can be scheduled initially \new{(static case)} and all these schedules remain valid until the end,
\new{when new schedules are computed in a dynamic way (with recomputation). However, only}
$16$ experiments end with a successful schedule without recomputation, a rate of~$5.5\%$.

@@

\new{
These results indicate that a meaningful comparison proves difficult due to
many invalid schedules. However, they still show that doing recomputation 
is beneficial for both the makespan and the number of valid solutions.
}
